### 2010-03-17 papers/icfp-2010-desc/paper_idesc.tex
Desc@ICFP: close some todos.
Desc@ICFP: more things todo, I'm afraid.
Desc@ICFP: fix dangling label
Desc@ICFP: clean-up \note{}s. Update todo.

\section{Indexing descriptions}

@@

However, this new class of objects cannot be defined by mere
induction. In the case of vectors, for instance, we have to define the
whole \emph{family} of vector in one go: vectors of all size needs to
be defined at the same time. Where simply-typed languages have
inductive types, we adopt inductive family of types as our basic
grammar of data-types. To this end, we rely on \emph{indexing}. We are
going to transform the $\Desc$ universe into an indexed $\IDesc$
universe. We express inductive families by the $I \To \IDesc{I}$ type.

@@

\note{ Actual implementation of forcing as a generic function??! }

>>>>

\section{Indexing descriptions}
\label{sec:indexing-desc}

@@

However, this new class of objects cannot be defined by mere
induction. In the case of vectors, for instance, we have to define the
whole \emph{family} of vector in one go: vectors of all size needs to
be defined at the same time. Where simply-typed languages have
inductive types, we adopt inductive family of types as our basic
grammar of data-types. To this end, we rely on \emph{indexing}. We are
going to transform the $\Desc$ universe into $\IDesc$, the universe of
indexed descriptions. We express inductive families by the $I \To
\IDesc{I}$ type.

@@
